Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-12-23 pkg/circtree/inst/wind_paper/draft/draft.Rnw
corrected typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2944 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 6db935ca10449570355f41c7a36cc63f0760daec

To conclude, in general the tree structure can capture nonlinear changes,
shifts, and potential interactions in covariates without prespecification of
such effects. As supported by the presented case study, this can be
particularly useful for modeling a highly fluctuating response, such as
typically observed for wind direction, or/and in case of a large number of
possible covariates. Moreover, the case study shows that building ensembles of
circular regression trees can even improve the forecasting performance, as the
resulting forests allow for modeling smooth effects and stabelize the model.

>>>>

To conclude, in general the tree structure can capture nonlinear changes,
shifts, and potential interactions in covariates without prespecification of
such effects. As supported by the presented case study, this can be
particularly useful for modeling a highly fluctuating response, such as
typically observed for wind direction, or/and in case of a large number of
possible covariates. Moreover, the case study shows that building ensembles of
circular regression trees can even improve the forecasting performance, as the
resulting forests allow for modeling smooth effects and stabilize the model.
